Borel regularity for ODEs and Thimble Integrals

### 2023-10-17 exp-resurgence.tex
Clean up revisions related to cond:sing
Typos correction, update to-do list

\title{Borel regularity for ODEs and thimble integrals}
\author{Veronica Fantini and Aaron Fenyes}

@@

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}

@@

\subsubsection{Why does Borel summation work for thimbles integrals?}

@@

\subsubsection{Setting}\label{setting-ODE}

Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
\begin{equation}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}

@@

For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
\begin{itemize}
\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$. In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $Omega_j$. Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    %\includegraphics{figures/u_contour_3.pdf}
    \includegraphics[scale=0.3]{figures/thimble_Airy.png}
    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the region indicate and what the color]}}
    \label{fig:path_Airy}
\end{figure}

@@

\subsection{Modified Bessel}

@@

\subsubsection{thimble projection formula}

@@

In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using a trigonometric substitution. As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time using applying the thimble projection formula to the generalized Cardano's formula.

@@

\textcolor{orange}{[add the numerical check to show simple resurgence]}

>>>>

\title{Borel regularity for ODEs and Thimble Integrals}
\author{Veronica Fantini and Aaron Fenyes}

@@

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE}---definitely Section~\ref{setting-ODE}, and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\label{reg-decay}
    \end{itemize}
    \item Replace {\tt reg-sing-volterra} with the citation from Arxiv
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
\end{brainstorm}

@@

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}
When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$. \textcolor{orange}{[Picture below should show the constant-radius neighborhood]}
\begin{center}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north east] at (\size, \size) {$z$};
\end{tikzpicture}
\end{center}

@@

\subsubsection{Why does Borel summation work for thimble integrals?}

@@

\subsubsection{Setting}\label{setting-ODE}
\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
\begin{equation}
\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
\end{equation}

@@

For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
\begin{itemize}
\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$. In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$. Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}
\end{itemize}

@@

\begin{figure}[ht]
    \centering
    %\includegraphics{figures/u_contour_3.pdf}
    \includegraphics[scale=0.3]{figures/thimble_Airy.png}
    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the regions indicate and what the color]}}
    \label{fig:path_Airy}
\end{figure}

@@

\subsection{Modified Bessel}\label{sec:mod-bessel-lift}

@@

\subsubsection{Thimble projection formula}

@@

In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using trigonometric substitution. As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time applying the thimble projection formula to the generalized Cardano's formula.

@@

\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of magnitude of function on position domain]}
